### 2016-05-24 intro.tex
intro hacking still

In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.  Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.  Let's assume the former, for the moment.  In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.  Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.  Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations. Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.

@@

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$, whatever their use, are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, it only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  They use the basic Bloom filter with four hash functions, used to populate the array and respond to queries, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $H_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.  This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.

>>>>

In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.  Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.  Let's assume the former, for the moment.  In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.  Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.  Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations. Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.

@@

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, it only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  They use the basic Bloom filter with four hash functions, used to populate the array and respond to queries, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $H_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.  This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
